SAYCAM preprocessing analyses from bounding box outputs

### 2022-01-06 preprocessing/step5_preprocess_fullset_from_bb_outputs.Rmd
update code to get center dets for gold sample

   # now get vid level data
   gold_sample_op <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
     group_by(frame, vid_name, child_id) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)

@@

   gold_sample_op<- gold_sample_op %>%
      right_join(gold_sample_op_center)[1:]

>>>>

   # now get vid level data
   gold_sample_op_all <- this_vid_data %>%
     filter(frame %in% frames_to_get$frame) %>%
     mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
     group_by(frame, vid_name, child_id) %>%
     summarize(hand_detected = sum(!is.na(mean_confidence[label=='hand']))>0,face_detected = sum(!is.na(mean_confidence[label=='face']))>0)

   # gold_sample_raw_dets <- this_vid_data %>%
   #   filter(frame %in% frames_to_get$frame) %>%
   #   mutate(vid_name = str_split(vid_name,"[.]")[[1]][1]) %>%
   #   group_by(frame, vid_name, child_id)

@@

   gold_sample_op<- gold_sample_op_all %>%
      left_join(gold_sample_op_center, by=c('vid_name','child_id','frame')) %>%
      mutate(hand_detected_center = replace_na(hand_detected_center, 'FALSE')) %>%
      mutate(face_detected_center = replace_na(face_detected_center, 'FALSE'))

   # compile vid-level summaries 
   if (vid_index == 1){
     all_gold_sample_frames_op <- gold_sample_op
     # gold_sample_all_dets <- gold_sample_raw_dets 
   }
   else if (vid_index > 1) {
   all_gold_sample_frames_op <- all_gold_sample_frames_op %>%
     full_join(gold_sample_op)

   # gold_sample_all_dets <- gold_sample_all_dets %>%
   #   full_join(gold_sample_raw_dets)

   }
}
}
}
}
```

# Save it out
```{r}
# gold sample individual detections for each frame with position data
save(gold_sample_all_dets, file = here::here('data/preprocessed_data_2021/',paste0('gold_sample_all_indiivdual_dets.RData')))

```{r}
